\documentclass{lnotes}
\usepackage{amsfonts}
\usepackage[mathscr]{euscript}

% Bibliography
\usepackage[style = alphabetic]{biblatex}
\addbibresource{references.bib}

% Packages
\usepackage{epigraph}
\usepackage[osf]{libertineRoman}
\usepackage{biolinum} % nice sans serif font
\usepackage{ulem} % for strikethrough text
\usepackage{outlines}
% \usepackage{tikz-cd}
% \usepackage{dsfont}
% \newcommand{\1}{\mathds{1}}
\newcommand{\B}{\mathcal{B}}
% \usepackage{wasysym}

% Enumitem environment
\newlist{steps}{enumerate}{1}
\setlist[steps, 1]{leftmargin=1.5cm, label = Step \arabic*:}

% Commands
\newcommand{\contains}{\supseteq}
\newcommand{\ts}{\textsuperscript}

% Operators
\DeclareMathOperator*{\diam}{diam}
\DeclareMathOperator*{\osc}{osc}

% Change equation numbering style
\numberwithin{equation}{section}

% Document Information
\title{Measure Theory and~Integration}
\course{\textsc{MATH} 320}
\place{Yale University} \term{Fall} \year{2022}

\blurb{
	These are lecture notes for \textsc{math} 320, ``Measure Theory and Integration'' taught by Charlie Smart at Yale University during the fall of 2022.
	These notes are not official, and have not been proofread by the instructor for the course.
	These notes live in my lecture notes respository at
	\[\text{\url{https://github.com/Eph97/Math320}.}\]
	If you find any errors, please open a bug report describing the error, and label it with the course identifier, or open a pull request so I can correct it.
}

\begin{document}

\section*{Syllabus}

\begin{center}
\begin{tabular}{@{}rp{10cm}@{}}
\toprule
\textbf{Instructor} &  Prof. Charlie Smart, \url{charlie.smart@yale.edu} \\
\textbf{Lecture} & MW 11:35 \textsc{am}--12:50 \textsc{pm}, Humanities Quadrangle 207 \\
\textbf{OH} & M 1:00 \textsc{pm}--3:00 \textsc{pm}, Dunham Lab 450 \\
% \textbf{Recitation} & TBA \\
\textbf{Textbook} & \fullcite{Rudin} \\
\textbf{Midterms} & Mon Oct 3, 2022 (In-Class) \\
				  & Mon Nov 7, 2022 (In-Class) \\
\textbf{Final} & Tue Dec 20, 2022 at 2pm (Location: TBD) \\
\bottomrule
\end{tabular} \\[3ex]
\end{center}

\subsection*{Course Description}
This course will provide a comprehensive introduction to measure theory.  We will start from real analysis and build from there.  The following topics will be covered.
\begin{itemize}
  \item Measure spaces
  \item Integrals on general measure spaces
  \item Product measures
  \item Integral representation of absolutely continuous measures
  \item Integral representation of linear functions
  \item Lebesgue measure
  \item Hausdorff measure and fractals
  \item Applications in dynamics
  \item Applications in probability theory
\end{itemize}

\subsection*{Course Format}
Approximately 2/3 of the material with be presented in lectures while the remaining 1/3 will be covered in the weekly homework assignments.

\subsection*{Prerequisites}
Math 305 or equivalent.

\subsection*{Assessments and Grading}
There will be ten homework assignments, two in-class midterms, and an in-person final, comprising 30\%, 40\%, and 30\%, respectively, of the total grade.

\include{class_notes/01}
\include{class_notes/02}
\include{class_notes/03}
\include{class_notes/04}
\include{class_notes/05}
\include{class_notes/06}
\include{class_notes/07}
\include{class_notes/08}
\include{class_notes/09}
\include{class_notes/10}
\include{class_notes/11}
\include{class_notes/12}
\include{class_notes/13}
\include{class_notes/14}
\include{class_notes/15}
\include{class_notes/16}
\include{class_notes/17}
\include{class_notes/18}
\include{class_notes/19}

\end{document}
