\section{ 2022-09-28 }


Reviewing: $(X,T)$ nice $\Lambda : C_c (X) \to \mathbb{R}$ positive linear

\begin{align*}
	m(U) &= \sup\{\Lambda(f) : 0 \leq f \leq \1_c\} \\
	m(A) &= \inf\{m(U) : U \contains  A\}
\end{align*} 

\begin{lemma}
	$\mu$, outer measure in  $(X,\mathcal{P}(X))$ and Borel $\subseteq$ Caratheodory.
\end{lemma}

\begin{lemma}
	restrict $m$ to Borel $\sigma$-algebra $\mathbb{B}$ so $(X, \mathcal{B}, m)$ is a positive measure space
\end{lemma}

\begin{lemma}
	For $f \in C_c (X)$, $\Lambda(f) = \int f dm$
\end{lemma}

\begin{proof}
	Use definition of $m$ and partition of unity

	Using the linearity of $\Lambda$ and  $\int dm$, we may assume $0 \leq f \leq 1.$

	Construct 
	 \begin{align*}
	    \Lambda (f) = ( \max f^+ ) \Lambda \left(\frac{f^+}{\max f^+}\right) - (\max f^- ) \Lambda \left(\frac{f^-}{max f^-} \right)
	\end{align*} 
	and same for $\int dm$


	Let $U = \{x \in X : f(x) > 0\}$. Note  $\bar{U}$ is compact and $m(U) < \infty$.

	Let  $\varepsilon = \frac{1}{N}$ for some large  $N \geq 1$.

	Let
	\begin{align*}
		E_k = f^{-1}\left( [ (k-1) \varepsilon, K \varepsilon]\right)
	\end{align*}
	replace $E_1$ with its closer $\bar{E}_1$ so that $U_k$ cover $\bar{U}_1$
	 \begin{align*}
	\sum_{K} (K -1) \varepsilon \1_{E_k} \leq f \leq \sum_{K} k \varepsilon \1_{E_k}
	\end{align*} 

	Since $E_k \in B$, we can choose $U_k \contains E_k$ open with $\delta >0 $ arbitrary.
	We then have
	\begin{align*}
		m(U_k) &\leq m(E_k) + \delta \quad \text{and} \\
		U_k &\leq f^{-1} ( [ 0, (k+1)\varepsilon))
	\end{align*} 

	Choose partition of unity: $g_k \in C_c(X)$ such that  $0 \leq g_k \leq \1_{U_k}$ and \\
	$\1_{\bar{U}} \leq \sum_{K} g_k \leq 1$ 
	Then:
	\begin{align*}
	\Lambda(f) &= \Lambda( \sum_{k} g_k f) \\
			   &=  \sum_{k} \Lambda( g_k f) \\
			   &\leq  \sum_{k} (k+1) \varepsilon \Lambda( g_k ) \\
			   &\leq  \sum_{k} (k-1) \varepsilon ( \mu( E_k ) + \delta ) \\
			   &\leq \sum_{k} (k-1) \varepsilon \mu( E_k ) + \sum_{k} (2 \varepsilon [ \mu (E_k) + \delta] + (k+1) + \delta) \\
			   &\leq \int \sum_{k} (k-1) \varepsilon \1_{E_k} dm + 2 \varepsilon  \mu( U_k ) + C N \delta  \\
			   &\leq \int f dm + 2 \varepsilon  \mu(\bar{U}) + C N \delta  \\
	\end{align*} There is a symmetric computation of other inequality.
\end{proof}




\begin{theorem}[Riesz-representation theorem]
	If $(X,T)$ is nice and  $\Lambda : C_c (X) \to \mathbb{R}$ positive linear, then there is a \underline{unique}. Positive measure $\mu$ on $(X,\mathcal{B})$ such that  $\Lambda(f) = \int f dm$
\end{theorem}

\begin{lemma}
	If $(X,T)$ nice,  $(X, \mathcal{B}, m)$ positive measure space, and $m(X) < \infty$, then m is \underline{regular}, that is
	\begin{align}
		m(A) &= \inf\{m(U) : \underset{open}{U} \contains A\} \\
			 &= \sup\{m(K) : \underset{compact}{K} \subseteq A\}
	\end{align} 
\end{lemma}

\begin{proof}
	let $S_{*} = \{A \in S: (1) \text{ holds for $A$} \}$
It is enough to show $S_{*}$ contains open sets and is closed under complement and countable union.

Since $\mathcal{B}$ is the smallest $\sigma$-algebra containing open sets, this implies $S \contains \mathcal{B}$

\begin{enumerate}
	\item[Step 1:] Suppose $U$ open, from monotonicity we have $m(U) = \inf\{m(V) : V \contains U \}$
		write: $U = \bigcup_j K_j$ with  $K_j \subseteq K_{j+1}$ compact.
		\begin{align*}
			m(U) = m(\bigcup_j K_j = \lim_{j \to \infty} m(K_j)
		\end{align*} .

		Conclude
		\begin{align*}
			m(U) = \sup\{m(K) : \underset{compact}{K} \subseteq U \}
		\end{align*}

	\item[Step 2:] Suppose $A \in S$, choose $\underset{open}{U} \contains A \underset{compact}{K}$
		so $U^{c} \subseteq A^{c} \subseteq K^{c}$ and $m(U \setminus K) = m(U \setminus A) +m (A \setminus K) < \varepsilon$

		Then
		\begin{align*}
			m(\underset{open}{K^{c}} \setminus \underset{}{U^{c}}) < \varepsilon
		\end{align*}
		Choose $\underset{compact}{G} \subseteq K^{c}$ so $m(^{c} \setminus G) < \varepsilon$. Then 
	\begin{align*}
		g \bigcap U^{c} \subseteq A^{c} &\subseteq K^{c} \quad \text{and} \\
	m(K^{c} \setminus (G \cap U^{c})) &\leq m(k^{c} \setminus V^{c}) + m(K^{c} \setminus G) \\
									 &< 2\varepsilon
	\end{align*} 	
\item[Step 3:]
	Finite unions (automatic):
	If \begin{align*}
		K_1 &\subseteq A_1 \subseteq U_1 \\
		K_2 &\subseteq A_2 \subseteq U_2, \quad \text{then} \\
		K_1 \cup K_2 &\subseteq A_1 \cup A_2 \subseteq U_1 \cup U_2
	\end{align*} 
\item[step 4:]
	Suppose $A_j \in S$, wts $\bigcup_j A_j \in S$. By steps 2 and 3, we may assume  $A_j$ disjoint.

	Next choose $K_j \subseteq A_j \subseteq U_j$ with  $m(U_j \setminus K_j) \leq \frac{\varepsilon}{2j}$ 

	Have $\cup_j K_j \subseteq \cup_j A_j \subseteq \cup_j U_j$ and  $m(\cup U_j \setminus \cup_j K_j ) \leq 2 \varepsilon$ 

	Then 
	\begin{align*}
		m( \cup)j U_j \setminus \cup_j K_j) &= \lim_{n \to \infty} m ( \cup_j U_j \setminus \cup K_j) \quad \text{choose finite $n$ so} \\
		K_1 \cup \ldots \cup K_n &\subseteq \cup_j A_j \subseteq \cup_j U_J \quad \text{and} \\
		m(\cup_j U_j &\setminus K_1 \cup \ldots \cup K_n )) \leq 3\varepsilon
	\end{align*} 
\end{enumerate}

\end{proof}

\begin{lemma}
	If $(X, T)$ nice, and $(X,\mathcal{B}, m)$ is a positive measure space, then
	\begin{align*}
		M(A) &= \inf\{m(U) : U \contains A\} \\
			 &= \sup \{m(K) : K \subseteq A \} \quad \text{whenever} \, A \in \mathcal{B},
			 \, A \subseteq U, \, m(U) < \infty
	\end{align*}
\end{lemma}

\begin{proof}
	Restrict to subspace $(U,T)$ and apply previous lemma.
\end{proof}

\subsection{uniqueness}
It remains to show the uniqueness of the Riesz measure: suppose $m_1$ and $m_2$ are positive measures on $(X,\mathcal{B})$ and $\int f dm_1 = \int f dm_2$ for some  $f \in C_c(X)$.


We want to show that it must be  $m_1 = m_2$

\begin{proof}
	Suppose $m_1 \neq m_2$
	 \begin{enumerate}
		 \item[step 1:] there is an open $U$ and $A \subseteq U$ with $m_1 (U) < \infty$, $m_2 (U) < \infty$, and $m_1 (A) \neq m_2(A)$

		 \item[step 2:] WLOG, $m_1(A) < m_2 (A).$ Since $m_1$ and $m_2$ are regular on $U$, choose 
			 \begin{align*}
				 &\underset{compact}{K} \subseteq A \subseteq \underset{open}{U} \quad \text{so} \\
				 &m_1 (A) \leq m_1 (U) < m_2 (K) \leq m_2 (A)
			 \end{align*} 
			 and Choose $f \in C_c (X)$ so $\1_K \leq f \1_U$.
			 We then obtain
			 \begin{align*}
				 m_2 (K) &\leq \int f dm_2 \\
					 &= \int f dm_1 \leq m_1 (U)
			 \end{align*} 
			 Contradicting (star)
	\end{enumerate}
\end{proof}


Next: $Q \subseteq \mathbb{R}^d$ closed rectangles.
\begin{align*}
\Lambda : C(Q) \to \mathbb{R} \quad \text{is} \\
\Lambda(f) = \int_{Q} f \quad \text{(Riemann)}
\end{align*} Then $\Lambda(f) = \int f dL$ where $L$ is the restriction of $L^*$ to Borel sets.
\subsection{Midterm 1 Review}
For the midterm on October 3rd, 2022, we should know basic definitions, basic examples and basic theorems. The following topics will be covered:
\begin{enumerate}
	\item Riemann integration
	\item Riemann integrability characterized on $L^*$ (Lebesgue outer measures)
	\item Measurable spaces
	\item Measurable functions
	\item Topological spaces
	\item Abstract integration
	\item Convergence Theorems (Monotone, Fatou's, Dominated Convergence)
	\item Borel measures
	\item Riesz theorem
	\item Outer measures, Caratheodory
\end{enumerate}
